---
title: "Lab 2"
---

```{r,include = FALSE}
## DO NOT DELETE THIS CHUNK
knitr::opts_chunk$set(error = TRUE)
```

### Enter the names of the group members here: 

**This assignment is due by the end of the lab. Only one student in the group submits a pdf file on Gradescope.**

*For all questions, include the R commands/functions that you used to find your answer (show R chunk). Answers without supporting code will not receive credit. Write full sentences to describe your findings.*

In this lab, you will explore the dataset `diamonds` contained in the package `ggplot2`. The `ggplot2` package is loaded when you load the `tidyverse` package so we can just load a single package.

```{r, warning=FALSE, message=FALSE}
## Load the tidyverse and ggplot2 packages together
library(tidyverse)
```

The `diamonds` dataset consists of prices and quality information from about 54,000 diamonds. The first few observations are listed below.

```{r}
## Print the first few rows of the 'diamonds' dataset
diamonds
```

This dataset is fairly large so it's not possible to examine every observation. But you can take a random sample of 10 rows using the `sample_n()` function.

```{r}
diamonds |> 
        sample_n(10)
```
Try taking a random sample of 15 rows from the dataset and check if anything seems out of the ordinary in those observations.

```{r}
# your code goes below (make sure to edit comment)
```


### Question 1: (1 pt)

Save the dataset `diamonds` in the environment and name it using the initials of all team members in alphabetical order. *Remember that you can get more details about the dataset by running `?diamonds` in the console.*

*Note: DO NOT use `?` in this document as that will prevent you from rendering it or will open the documentation in a new tab.*

```{r}
# your code goes below (make sure to edit comment)

```

------------------------------------------------------------------------

### Question 2: (4 pts)

Use this template of a `ggplot` command to create a histogram of `price`:

```{r}
# EDIT: Histogram using ggplot
dataset |> 
        ggplot(aes(x = variable)) + 
        geom_histogram() 
```

Use this template of a `ggplot` command to create a boxplot of `price`:

```{r}
# EDIT: boxplot using ggplot
dataset |> 
        ggplot(aes(x = variable)) + 
        geom_boxplot() 
```

Comparing the boxplot to the histogram, in your view, which visualization is more informative for understanding the distribution of the `price` data?

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 3: (3 pts)

Use this template of a `ggplot` command to create a bar graph of `clarity`:

```{r}
# EDIT: Bar graph using ggplot
dataset |> 
        ggplot(aes(x = variable)) + 
        geom_bar() 
```


Using these plots, what is the most common category of `clarity`?

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 4: (4 pts)

An important parameter for histograms is the number of bars that you use in the plot. This is set using the `bins` argument to `geom_histogram()`. The default is `bins = 30`. What happens if you use just 5 bins for the histogram of `price`? Or what about using 45? How do the histogram look different from each other?

```{r}
# your code goes below (make sure to edit comment)

```

**Your answer goes here. Write sentences in bold.**

------------------------------------------------------------------------

### Question 5: (3 pts)

We actually discussed a function in lecture that can create a graph for each category of a variable using `ggplot`. Using `ggplot` with that function, create a histogram of price for each category of clarity.

```{r}
# your code goes below (make sure to edit comment)

```


------------------------------------------------------------------------

### Question 6: (3 pts)

Choose one question about that the data that you want to investigate (could be the one from the pre-Lab Quiz). Write two hypotheses related to this question using a numbered list below:

1. 

2. 

Make a plot that addresses that question and is informative for the hypotheses you have chosen. How would you interpret the results of the plot? Which o the two hypotheses is more likely?


```{r}
# your code goes below (make sure to edit comment)

```



**Your answer goes here. Write sentences in bold.**


------------------------------------------------------------------------


### Formatting: (2 pts)

Comment your code, write full sentences, and knit your file!
